Introductory Physics Labs: A Tale of Two Transformations

### 2020-10-07 manuscript/onlineLabPaper.tex
Small typographic changes to main MS

Labs are supervised by Author 2, but sections are run by Graduate GTAs (GTAs). The
transformed curriculum was jointly written by both of the authors.  GTA training was also greatly
enhanced when the new lab curriculum was put in place.  Both authors, along with colleagues in
Biology and Chemistry, run training for all GTAs in Biology, Chemistry, Geology, and Physics
as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
weekly prep meeting with the GTAs, and Author 1 and the research team have supervised various
aspects of the transformation especially important for research such as curricular
implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019mask}.

@@

The argumentation session was held in a scheduled Cisco WebEx session
the week after the proposal session. Before this session, each group was required to complete
its analysis and create a three-slide presentation for the argumentation session: (1) a description of their measurements, (2) a presentation of the
results, including a graph or table, and (3) their argument based on their
results.  One member of each group gave the presentation, which was followed by
questions. Students received credit for giving presentations, asking meaningful questions, and
responding to questions.  Following the argumentation session, students submitted individual
draft reports, peer-reviewed each other's drafts, and submitted final reports in the same
manner used for the face-to-face investigations.

@@

We developed lab kits with supplies that allowed students to perform the investigations outside
the teaching laboratory so we could provide students with a hands-on experience. We purchased
the lab kit items in collaboration with our campus bookstore, and the students purchased the
lab kits from the bookstore. We ordered lab kit items in bulk and where possible directly from
manufacturers to reduce the costs of the items. Each Physics 1 kit cost \$20.60 and each
Physics 2 kit cost \$39.00. Students payed for these kits in place of a lab manual, which we
provide online for this course.  The online adaptation of the face-to-face ADI curriculum has
changed slightly. Pre-labs are done in groups asynchronously.  Proposals are developed in
groups during the lab period, and scheduled argumentation sessions occur via WebEx during the
lab period.

>>>>

Labs are supervised by Author 2, but sections are run by Graduate TAs (GTAs). The
transformed curriculum was jointly written by both of the authors.  GTA training was also greatly
enhanced when the new lab curriculum was put in place.  Both authors, along with colleagues in
Biology and Chemistry, run training for all GTAs in Biology, Chemistry, Geology, and Physics
as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
weekly prep meeting with the GTAs, and Author 1 and the research team have supervised various
aspects of the transformation especially important for research such as curricular
implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019mask}.

@@

The argumentation session was held in a scheduled WebEx session
the week after the proposal session. Before this session, each group was required to complete
its analysis and create a three-slide presentation for the argumentation session: (1) a description of their measurements, (2) a presentation of the
results, including a graph or table, and (3) their argument based on their
results.  One member of each group gave the presentation, which was followed by
questions. Students received credit for giving presentations, asking meaningful questions, and
responding to questions.  Following the argumentation session, students submitted individual
draft reports, peer-reviewed each other's drafts, and submitted final reports in the same
manner used for the face-to-face investigations.

@@

We developed lab kits with supplies that allowed students to perform the investigations outside
the teaching laboratory so we could provide students with a hands-on experience. We purchased
the lab kit items in collaboration with our campus bookstore, and the students purchased the
lab kits from the bookstore. We ordered lab kit items in bulk and, where possible, directly from
manufacturers to reduce the costs of the items. Each Physics 1 kit cost \$20.60 and each
Physics 2 kit cost \$39.00. Students payed for these kits in place of a lab manual, which we
provide online for this course.  The online adaptation of the face-to-face ADI curriculum has
changed slightly. Pre-labs are done in groups asynchronously.  Proposals are developed in
groups during the lab period, and scheduled argumentation sessions occur via WebEx during the
lab period.
